Appendix 2: Example of index standardization of fishery-independent survey data with sdmTMB

### 2022-01-14 doc/appendix-pcod-sdmTMB.Rmd
fix typo

The above example used the default `bias_correct = FALSE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more detils can be found in the  [TMB documentation](https://github.com/kaskr/adcomp/wiki) or [@thorson2016bias]. Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements a generic bias correction algorithm that should correct for this, but can take considerable time and memory.

>>>>

The above example used the default `bias_correct = FALSE` in `get_index()`. The `bias_correct` argument is a feature of TMB for models with random effects, and more details can be found in the [TMB documentation](https://github.com/kaskr/adcomp/wiki) or [@thorson2016bias]. Leaving `bias_correct = FALSE` is fine for experimentation or a quick example, but will be biased due to the nonlinear (`exp()`) transformation of the random effects. Setting `bias_correct = TRUE` implements a generic bias correction algorithm that should correct for this, but can take considerable time and memory.
